# Creating R package

```{r, include=FALSE}
library(tidyverse)
library(devtools)
library(neattools)
```

To prove my abilitiy to create an R package, I have created a package called "neattools", neattools is a package that helps you manipulate data in a dataframe.

```{r, eval = FALSE}
devtools::install_github("timovoskuilen/neattools", build_vignettes = TRUE)
```

for the creation of this package, the mtcars dataset, which is a build in R dataset, is used. Also, attached to the package is a dataset called layout, which is a dataset containing a made up 384 wells plate layout for drug screening.

__Functions__

This package includes 4 functions, which will all be shown including examples below.

The function __flip__ flips the columns and rows from a dataframe:
```{r, message = FALSE}
head(mtcars, n = 2)
flip(head(mtcars, n = 2))
```

the function __ removecolumn__ lets you remove a specific column from a dataframe
```{r, message = FALSE}
head(layout, n = 2)
removecolumn(head(layout, n =2), "Drug")
```

the function __subset__ lets you subset specific rows from a  dataframe
```{r, message = FALSE}
head(layout, n = 2)
subset(head(layout, n = 2), 1)
```

the function __replacevalue__ lets you replace a specific value in a dataframe
```{r, message = FALSE}
head(layout, n = 5)
replacevalue(head(layout, n = 5), "Drug", "Analyfyn", "Test")
```